Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-08 manuscript/manuscript.tex
changes

We've calculated the convergent correlation for all rows of the replicate
covariance matrices. Like temporal covariances, we visualize these through time
(Figure \ref{fig:figure-2} A), with each line representing the convergent
correlation from a particular reference generation $s$ as it varies with $t$
(shown on the x-axis). In other words, each of the colored lines corresponds to
the like-colored row of the convergence correlation matrix (upper left in
Figure \ref{fig:figure-2} A). We find these convergent covariances are
relatively weak, and decay very quickly from an initial value of about 0.1
(95\% block bootstrap confidence intervals $[0.094, 0.11]$) to around 0.01
(95\% CIs [0.0087, 0.015]) within 20 generations. This is consistent with
the primary finding of the original \textcite{Barghi2019-qy} study: that
alternative loci contribute to longer term adaptation in different
replicates.  \vb{We note that convergent correlation for the last timepoint
is abnormally high; this is not in fact driven by a single outlier pair of
covariances but all our high for reasons unknown to us.}

@@

  \caption{{\bf A}: The convergence correlation, averaged across replicate
    pairs, through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
    line corresponds to a row of the temporal convergence correlation matrix
    depicted to the right.  {\bf B}: The convergence covariance between
    individual pairs of replicates in the \textcite{Kelly2019-dc} data. {\bf
    C}:  The convergence covariance between individual pairs of replicates in
    \parencite{Castro2019-uk} data, for the two selection lines  (LS1 and LS2)
    and the control (Ctrl); gray CIs are those using the complete dataset, blue
    CIs exclude chromosomes 5 and 10 which harbor the two regions
    \textcite{Castro2019-uk} found to have signals of parallel selection between
    LS1 and LS2.}

@@

A benefit of between-replicate covariances is that unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed us to assess the impact of linked selection in
driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate wild populations of
\emph{Drosophila simulans} for 14 generations adapting to a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistically significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$). \vb{Similarly, we can
  calculate the proportion of the total variance in allele frequency change
  from convergent selection pressure analogous to $G$ where the numerator is is
  the convergent covariance and the denominator is the total variance (see
  XXX). We find that 37\% of the total variance is due to shared allele
frequency changes caused by selection (95\% CI [29\%, 41\%]; these are similar
to the convergence correlation, see XXX).}

@@

\subsection{\textcite{Barghi2019-qy} Trimmed Window Covariances}

 \begin{table}
   \centering
   \footnotesize
   \centering
   \begin{tabular}{l c c c c c c}
     s & t & 5\% CI & median & 95\% CI & trimmed mean \\ \hline

>>>>

We've calculated the convergent correlation for all rows of the replicate
covariance matrices. Like temporal covariances, we visualize these through time
(Figure \ref{fig:figure-2} A), with each line representing the convergent
correlation from a particular reference generation $s$ as it varies with $t$
(shown on the x-axis). In other words, each of the colored lines corresponds to
the like-colored row of the convergence correlation matrix (upper left in
Figure \ref{fig:figure-2} A). We find these convergent covariances are
relatively weak, and decay very quickly from an initial value of about 0.1
(95\% block bootstrap confidence intervals $[0.094, 0.11]$) to around 0.01
(95\% CIs [0.0087, 0.015]) within 20 generations. This \gc{suggests
  that while a reasonable fraction of the initial response is shared over the
  replicates while the rapid decay} is consistent with
the primary finding of the original \textcite{Barghi2019-qy} study: that
alternative loci contribute to longer term adaptation in \gc{the} different
replicates.

@@

  \caption{{\bf A}: The convergence correlation, averaged across \gc{\textcite{Barghi2019-qy}} replicate
    pairs, through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
    line corresponds to a row of the temporal convergence correlation matrix
    depicted to the right.  \gc{We note that convergent correlation
      for the last timepoint is an outlier; we are unsure as to the cause of this, e.g. it does not appear to be driven by a single pair
of replicates.} {\bf B}: The convergence covariance between
    individual pairs of replicates in the \textcite{Kelly2019-dc} data. {\bf
    C}:  The convergence covariance between individual pairs of replicates in
    \parencite{Castro2019-uk} data, for the two selection lines  (LS1 and LS2)
    and the control (Ctrl); gray CIs are those using the complete dataset, blue
    CIs exclude chromosomes 5 and 10 which harbor the two regions
    \textcite{Castro2019-uk} found to have signals of parallel selection between
    LS1 and LS2.}

@@

A benefit of between-replicate covariances is that unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed us to assess the impact of linked selection in
driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate wild populations of
\emph{Drosophila simulans} for 14 generations adapting to a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistically significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$). Similarly, we can
  calculate the proportion of the total variance in allele frequency change
  from convergent selection pressure analogous to $G$ where the numerator is is
  the convergent covariance and the denominator is the total variance (see
  XXX). We find that 37\% of the total variance is due to shared allele
frequency changes caused by selection (95\% CI [29\%, 41\%]; these are similar
to the convergence correlation \gc{as the variances are relatively
  constant across replicates, see {\bf XXX}).}

@@

\subsection{\textcite{Barghi2019-qy} Trimmed Window Covariances}
\gc{ Here we report median and trimmed mean of the windowed covariances. We note that
  the median covariance is also limiting result of a trimmed
  mean that symmetrically excludes the upper and lower $\alpha$ tails to calculate the
 trimmed average windowed covariance. As $\alpha$ increases to 0.5, the
  trimmed covariance converges to the median windowed covariance (by the
 definition of the median; see Supplementary Figure
  \ref{suppfig:barghi-trimmed-mean}). Thus our genomic temporal covariances are
  non-zero due to the impact of selection on many genomic windows.  }
 \begin{table}
   \centering
   \footnotesize
   \centering
   \begin{tabular}{l c c c c c c}
     s & t & 5\% CI & median & 95\% CI & trimmed mean \\ \hline
